\section{Programming language and frameworks}

\subsection{Python}
Python is a  object-oriented programming language and it is used to develop the experiments necessaries is Python, more specifically, it has been used the 2.7 Python version.

\subsection{Theano and others frameworks}
Theano is the main framework used to develop the deep learning code. But others libraries has been used to, NumPy,Scikit-learn and matplotlib are the most relevant. In addition to this, other Python packages has been used to like Pickle.

\subsubsection{Theano}
Theano \cite{theano} is a Python library that allows users to work with mathematical expressions and work with simbolic variables, moreover, Theano handles multidimensional arrays efficiently. This framework has been used in order to build convolutional neural networks architecture and its training procedure.\\

There are numerous open-source deep-libraries that have been built on top of Theano, for example Keras, Lasagne and Blocks. Although the usability of using those libraries in stead of Theano is bigger, Theano is more flexible when user wants to develop its own layer, for example.\\

Theano is not the unique language oriented to deep learning, for example Google, has developed its deep learning language called TensorFlow; Caffe and Torch are others examples.\\

Theano main page is available in \url{http://deeplearning.net/software/theano/} where the documentation, examples,.. could be found.\\

\subsubsection{NumPy, Scikit-learn and Matplotlib}
NumPy is a Python library that provides a multidimensional array object, various derived objects (such as masked arrays and matrices), and an assortment of routines for fast operations on arrays, including mathematical, logical, shape manipulation, sorting, selecting, I/O, discrete Fourier transforms, basic linear algebra, basic statistical operations, random simulation and much more. The documentation of this library is available in \url{https://docs.scipy.org/doc/numpy/}.\\

Scikit-learn is an open source Python library and commercially usable that implements a range of machine learning, preprocessing, cross-validation and visualization algorithms which has been build in top of Numpy and matplotlib. Its documentation is available in the following url \url{http://scikit-learn.org/dev/index.html}.\\

Matplotlib is a python library for 2D plotting.
