\documentclass[a4paper]{article}

\usepackage[british,UKenglish,USenglish,english,american]{babel}
\usepackage{inputenc}


\begin{document}
\title{Face verification papers}
\maketitle

\section{A Convolutional Neural Network Approach for Face Verification}

\subsection{Intro}
Face verification (or authentication), on the other hand, is to determine if two face images belong to the same person. A global predefined threshold is required to make a decision that discriminates between the subjects.\\

Authors propose an improved version of the Siamese CNN architecture for the face verification task.\\

Each CNN is reduced to four layers, and it is used 2D discrete cross-correlation instead of 2d discrete convolution in the conv. layer.\\ 

\subsection{Proposed Architecture}
Authors fusion convolutional and subsampling layers. The main principle is cpncolve with a stride of 2or more with a convolution kernel. \\

It is used cross- correlation instead of convolution.\\

Prediction is performed by searching the combination of variables that minimizes the energy. So, the goal is search the optimal W that minimizes the loss function. For simpler computation, it is used L1 norm as similarity measure.\\

\subsection{Data Preparation and partitioning}
Authors use AT\&T face database with images of size 112x92 pixels. Images are cropped to a 92x92 window size and resized to 46x46.\\

It is used 320 face images for training and 40 for testing.\\

\subsection{Architecture details and training protocol}
The siamese architecture consistes of two identical CNN with shared weights, which are combined with a cost module that acts as a classifier.\\

The first conv layer performs 6x6 fused conv/subsampling operations that generates 5 21x21 maps.\\

The second conv layer uses a 6x6 fused conv/subsampling which produces 14 features maps.\\

The optput of the second conv layer is convolved with 6x6 trainable kernels  and fully connected to 60 neurons.\\

Next layer is a fully connected layer of 40 neurons. The output of this layer is used by the cost module which calculates the similary of the two vectors (1 per CNN).\\

Weighs and biases are randomly initialize by gausian distribution with mean value of 0 and deviation of 0.05.\\

\section{DeepFace: Closing the Gap to Human-Level Performance in Face Verification}

\subsection{Architecture and Training}

A 3D aigned 3-channels face image size of 152x152 pixels is theinputof the CNN. The first layer is a convolutional layer of 32 filtes of 11x11x3, resulting 32 features maps. The resulting 32 maps are fed to a max-pooling layer which takes  3x3 spatial neighbourhood with a stride of 2.\\

Next layer is another convolutional layer that has 16 filters of size 9x9x16 ( to extract low -level features).\\

The subsequent layers are instead locally connected, like a convolutional layer they apply a filter bank, but every location in the feature map learns a different set of filters (no sé muy bien que quiere decir esa frase). The last layer is fed by 74x74x3 patch.\\

The last layers are two fully connected layers.\\

The output of the las fully-connected layer is fed ot a k-way softmax which produces a distribution over the class labels.\\

The loss is minimized by stochastic gradient deent and the gradients are computed by standar backpropagation error.\\

Authors use ReLu activation function which is applied after every  convolution, locally connected and fully connected layer (except last one).\\

It has been aplied dropout only in the first fully connected layer .\\

Features are normalized between zero and one. to reduce the sensivity to illumination changes.

\subsection{Datasets}
There are some databases which haws been used:

\begin{enumerate}
\item The SFC dataset
\item The LFW dataset
\item The Youtube face dataset

\end{enumerate}


\section{•}

\end{document}

