\documentclass[a4paper]{article}

\usepackage[british,UKenglish,USenglish,english,american]{babel}
\usepackage{inputenc}
\usepackage{url}


\begin{document}
\title{Face Databases}
\maketitle

\section{The Labeled Faces in the Wild}

\textit{The Labeled Faces in the Wild} is a well-known and used dataset of faces images that can be found in its official web page \url{http://vis-www.cs.umass.edu/lfw/}.\\

\subsection{Properties}
The characteristics of this dataset are the following ones:
\begin{itemize}
 \item Number of samples/ Number of images : 13233
 \item Number of features/ length of each vectorized image: 187500
 \item Number of classes / Number of people: 5748\\
\item The number of images per person is not the same for each one.
\item The size of each image is 250x250 pixels.
\item The images are RGB ones.
\item The faces in images are in the center of the image.\\
\end{itemize}


\section{Yale face database}
The \textit{Yale face database} could be found in the next url \url{http://vision.ucsd.edu/content/yale-face-database}.

This database has the following characteristics provided by authors:
\begin{itemize}
\item contains 165 grayscale images in GIF format of 15 individuals. \item There are 11 images per subject, one per different facial expression or configuration: center-light, w/glasses, happy, left-light, w/no glasses, normal, right-light, sad, sleepy, surprised, and wink.
\end{itemize}

\section{The Collection of Facial Images}
This database could be found in \url{http://cswww.essex.ac.uk/mv/allfaces/index.html}. The database is composed of four different database with different number of people or different size of images among database.

In general, the database has the following characteristics which are provided by authors:

\begin{itemize}
\item Total number of individuals: 395
\item Number of images per individual: 20
\item Total number of images: 7900
\item Gender:  contains images of male and female subjects
\item Race:  contains images of people of various racial origins
\item Age Range:  the images are mainly of first year undergraduate  students, so the majority of indivuals are between 18-20 years old but some older individuals are also present.
\item Glasses: Yes
\item Beards: Yes
\item Image format: 24bit colour JPEG
\item Camera used: S-VHS camcorder
\item Lighting: artificial, mixture of tungsten and fluorescent overhead

\end{itemize} 

\section{Georgia Tech face database}
Georgia Tech face database \url{http://www.anefian.com/research/face_reco.htm}

\begin{itemize}
\item Contains images of 50 people.
\item There are 15 color JPEG images with cluttered background per person.
\item The resolution is 640x480 pixels. 
\item The average size of the faces in these images is 150x150 pixels.
\item The pictures show frontal and/or tilted faces with different facial expressions, lighting conditions and scale. Each image is manually labeled to determine the position of the face in the image. T
\end{itemize}



\end{document}